\chapter{Requirements}
\label{app:RE}

This section contains all requirements for the developed application. It limits on the \textit{description}, \textit{title} and \textit{id} of the requirements to save space.

\section{Functional Requirements}
This section describes all functional requirements of the application.

\subsection{Database}
\paragraph{R001 Database}
The application stores all demanded informations in a database.
\paragraph{R018 Project Database}
It exists a database where all projects are stored.
\paragraph{R002 Project Database: Restriction}
For the Bachelor Thesis the application only got a local database.
\paragraph{R057 Delete Flag}
Deleted projects get a deletion flag before deleting them completely.
\paragraph{R058 Erase Deleted Projects}
Projects with a deletion flag can be erased from the database.
\paragraph{R059 Stored Property Parameters}
The parameters for each property are stored in the database.
\paragraph{R060 Property Distance Informations}
The database contains all informations to calculate the distance of projects.
\paragraph{R061 View Deleted Projects}
It is possible to view all projects with deletion flag.
\paragraph{R063 Recover Projects}
It's possible to recover projects with a deletion flag.
\paragraph{R064 Database Size}
The application allows to view the physical size of the database in \texttt{mb}.

\subsection{Projects}
\paragraph{R004 Projects Overview}
The application must have an overview where all projects are displayed.
\paragraph{R005 Filter Projects}
In the projects overview the user has the possibility to filter the project properties.
\paragraph{R006 Sort Projects}
In the projects overview the user has the possibility to sort the projects properties.
\paragraph{R007 Sort Projects: Standard Sort}
The Standard  sort method for the projects is the creation date.
\paragraph{R008 Search Project}
In the project Overview exists the possibility to search a project.
\paragraph{R072 Sort Last Edited}
It is possible to sort the project after the last edited date.
\paragraph{R073 Sort Name}
It is possible to sort the projects after name.

\subsubsection{Project Creation}
\paragraph{R023 Create Project}
It is possible to create a new project in the application
\paragraph{R024 Create Project: Project Name}
To create a Project a new Name must set
\paragraph{R025 Create Project: unique ID}
All Projects have an unique ID.
\paragraph{R026 Create Project: Set Estimation Method}
To create a Project an available estimation method must be set
\paragraph{R027 Create Project: Load Project Influence Factors}
After an Estimation Method is set the influencing factors are loaded
\paragraph{R028 Create Project: Set Influencing Factors}
All Influence Factors need to be set to complete the creation process
\paragraph{R029 Create Project: Project Phase}
For the creation Process the actual Project Phase can be set
\paragraph{R030 Create Project: Project Properties}
There has to be the possibility to add existing project properties
\paragraph{R031 Create Project: Development Market}
The development market of the Project is selectable 
\paragraph{R032 Create Project: Development Kind}
The development kind of the Project is selectable 
\paragraph{R033 Create Project: Process Methodology}
The process methodology of the Project is selectable 
\paragraph{R034 Create Project: Programming Language}
The programming language of the Project is selectable 
\paragraph{R035 Create Project: Platform}
The platform of the Project is selectable 
\paragraph{R036 Create Project: Industry Sector}
The industry sector of the Project is selectable 
\paragraph{R037 Create Project: Architecture}
The architecture of the Project is selectable 
\paragraph{R038 Create Project: Project Icon}
The project icon of the Project is selectable 
\paragraph{R039 Create Project: Guided Creation Process}
It is possible to start a guided creation for the project which guides the user through each step.
\paragraph{R040 Create Project: List Creation}
It is possible to create a new project with a list creation which inherits all properties for the creation
\paragraph{R041 Create Project: Long Project Name}
Project names have to be limited to 40 characters
\paragraph{R042 Create Project: Preselected Properties}
One value must be preselected for all properties.
\paragraph{R043 Create Project: description}
It should be possible to add a project description
\paragraph{R044 Create Project: Property Sorting}
All Properties are sorted alphabetically descending for the selection
\paragraph{R045 Create Project: Suggest Estimation Method}
There should be the possibility to calculate the best fitting estimation method for the project
\paragraph{R046 Create Project: Suggest Estimation Method - Sorting}
The suggested methods are sorted after the best fitting.
\paragraph{R071 Guided Creation - Progress}
The progress of the guided creation is visible.
\paragraph{R072 Cancel Project Creation}
If the user cancels the creation he will be warned that unsaved data will not be saved.

\subsubsection{Project Properties}
\paragraph{R010 Project Properties}
Each project has properties
\paragraph{R011 Project Properties View}
It is possible to get a view of all properties of a project.
\paragraph{R012 Saving Project Properties}
All properties are saved in the database.
\paragraph{R050 Property: Development Market}
All projects contain the property for development market.
\paragraph{R051 Property: Development Kind}
All projects contain the property for development kind.
\paragraph{R052 Property: Process Methodology}
All projects contain the property for process methodology.
\paragraph{R053 Property: Programming Language}
All projects contain the property for programming language.
\paragraph{R054 Property: Platform}
All projects contain the property for platform.
\paragraph{R055 Property: Industry Sector}
All projects contain the property for industry sector.
\paragraph{R056 Property: Software Architecture}
All projects contain the property for software architecture.
\paragraph{R071 Automatic Save}
Changes on project properties are saved automatically.

\subsubsection{Project Estimation}
\paragraph{R014 Estimation}
An Estimation of projects is possible in all implemented estimation techniques.
\paragraph{R076 Function Point Estimation}
An estimation with the function point technique is possible.
\paragraph{R077 Function Point Estimation - Calculation Total Points}
The Total Points of the estimation will be calculated automatically
\paragraph{R078 Function Point Estimation - Calculation Evaluated Points}
The Evaluated Points of the estimation will be calculated automatically with the set influence factor.
\paragraph{R079 Function Point Estimation - Calculation Man Days}
The man days will be calculated automatically for the estimation.
\paragraph{R080 Man Days Calculation}
The man days will be calculated with a basis factor if no terminated project is available.
\paragraph{R081 Adapted Man Days Calculation}
If terminated projects exists, the man days will be calculated with an average points-per-day value.
\paragraph{R082 Change Influence Factor Set}
It is possible to change the set of influence factors of a project.
\paragraph{R083 Terminate Project}
Each estimation must allow a termination of the project.
\paragraph{R084 Editing After Termination}
A terminated project cannot be edited.
 
\subsection{Influence Factors} 
\paragraph{R085 Create New Influence Factor}
The application allows the creation of a new influence factor set.
\paragraph{R086 Influence Factor Name}
Each influence factor must contain a name.
\paragraph{R087 Influence Factor Empty Name}
The name for an influence factor must not be an empty string.
\paragraph{R088 Influence Factor ID}
Each influence factor set must have an unique id.
\paragraph{R089 Influence Factor Selection}
All Influence Factors are sorted after the estimation technique.
\paragraph{R090 Delete Influence Factor}
A created influence factor set can be deleted.
\paragraph{R091 Edit Influence Factor}
A created Influence Factor set can be edited.
\paragraph{R092 Influence Factor Sum}
The sum of the factor can be shown.

\subsection{Related Projects}
\paragraph{R009 Find Related Projects}
It must be possible to find related projects.
\paragraph{R010 Load Components From Other Projects}
It is possible to copy Components from other projects into the actual project.
\paragraph{R013 Project Properties Distance}
The distance of two projects is calculated with all project properties.
\paragraph{R065 Project Relevance}
The project relevance to the selected project is given in percentage.
\paragraph{R066 Related Projects Sorting}
All related projects are sorted descending after their relevance.
\paragraph{R067 Related Project Property}
It is possible to view the properties of a related project.
\paragraph{R068 Relation Border}
Only projects with a relevance more than 50\% are viewed.
\paragraph{R069 Show All Related Projects}
The application allows the option to show the relation to all projects.
\paragraph{R070 Properties of Related Projects}
It is possible to show the properties of a related project.

\subsection{Export}
\paragraph{R015 Export Project}
The application allows an exportation of projects to external files.
\paragraph{R074 Export XLS}
An export to xls format is possible.
\paragraph{R075 Open Exported XLS file}
The exported xls file will be opened when it is done.

\subsection{Help}
\paragraph{R016 Help Method}
The application inherits articles that provide informations to the user.
\paragraph{R093 Search Articles}
It is possible to search help articles.
\paragraph{R094 Selected Articles}
On the main help screen is only a selection of help articles visible.
\paragraph{R095 Show all articles}
It is possible to show all available articles on the screen.
\paragraph{R096 Open Articles}
A help article can be opened.
\paragraph{R097 Shown Articles}
The help articles are only shown with their title.
\paragraph{R098 Feedback}
The help screen allows sending of a feedback to the producer of the application.

\subsection{User Informations}
\paragraph{R017 Saving User Informations}
The application stores all necessary user informations in a database.
\paragraph{R099 Set User Name}
It is possible to set the user name.
\paragraph{R100 Password}
It' possible to set the password.
\paragraph{R101 User Name Length}
The user name length is limited to 30 characters.
\paragraph{R102 Password Length}
Password length is limited to 30 characters.
\paragraph{R103 Check Login}
It is possible to verify the login information.
\paragraph{R104 User Information}
All user information can be displayed.

\subsection{Feedback}
\paragraph{R019 Send Support Request}
The application provides the possibility to send a support request to the producer of the application.

\subsection{Synchronization}
\paragraph{R105 Sync Frequency}
It is possible to set the frequency for automatic synchronization.
\paragraph{R106 Automatic Sync}
The application allows to change via automatic and manual synchronization.
\paragraph{R107 Connection}
A selection which with which connection an automatic synchronization is possible is provided by the application.

\subsection{Miscellaneous}
\paragraph{R108 App Information}
The app provides a screen with all app information.
\paragraph{R109 Version Number}
The App Information shows the actual version number.
\paragraph{R110 License}
All license information can be viewed inside the application.
\paragraph{R111 Crash Reports}
All crash reports can be send to the server.
\paragraph{R112 Automatically Send Crash Reports}
It is possible to send crash reports automatically.

\section{Non-Functional Requirements}
This section describes all non-functional requirements of the application.
\paragraph{R003 Project Database: Normalization}
The database is normalized in the 3 normalization form.
\paragraph{R009 Design Guidelines}
The application must fulfills the Design Guidelines from Google - Material Design.
\paragraph{R010 Save Changes Automatically}
All changes in the application need to saved automatically.
\paragraph{R046 Crash safety}
The application does not crash if data was not found
\paragraph{R047 Error Information}
If an error occurs the application provides the user with a helpful error message.
\paragraph{R113 View Orientation Data Loss}
By changing the phone orientation no data must be lost.
\paragraph{R114 Main Language}
The main language for the application is English.
\paragraph{R115 Code Annotation}
All annotations of the source code are made in English.
\paragraph{R116 Method Annotations}
Each source code method and class have an annotation that describes the use.