\chapter{Requirements}
\label{app:RE}

This section contains all requirements for the developed application. It limits on the \textit{description}, \textit{title} and \textit{id} of the requirements to save space.

\section{Functional Requirements}
This section describes all functional requirements of the application.

\subsection{Database}
\paragraph{R001 Project Database}
It exists a database where all projects are stored.
\paragraph{R002 Project Database: Restriction}
For the Bachelor Thesis the application only got a local database.
\paragraph{R003 Project Database: Normalization}
The database is normalized in the 3 normalization form.

\subsection{Projects}
\paragraph{R004 Projects Overview}
The application must have an overview where all projects are displayed.
\paragraph{R005 Filter Projects}
In the projects overview the user has the possibility to filter the project properties.
\paragraph{R006 Sort Projects}
In the projects overview the user has the possibility to sort the projects properties.
\paragraph{R007 Sort Projects: Standard Sort}
The Standard  sort method for the projects is the last edit date.
\paragraph{R008 Search Project}
In the project Overview exists the possibility to search a project.

\subsubsection{Project Creation}
\paragraph{R023 Create Project}
It is possible to create a new project in the application
\paragraph{R024 Create Project: Project Name}
To create a Project a new Name must set

\paragraph{R025 Create Project: unique ID}
All Projects have an unique ID.

\paragraph{R026 Create Project: Set Estimation Method}
To create a Project an available estimation method must be set

\paragraph{R027 Create Project: Load Project Influence Factors}
After an Estimation Method is set the influencing factors are loaded

\paragraph{R028 Create Project: Set Influencing Factors}
All Influence Factors need to be set to complete the creation process

\paragraph{R029 Create Project: Project Phase}
For the creation Process the actual Project Phase must be set

\paragraph{R030 Create Project: Project Properties}
There has to be the possibility to add existing project documents

\paragraph{R031 Create Project: Development Market}
The development market of the Project is selectable 

\paragraph{R032 Create Project: Development Kind}
The development kind of the Project is selectable 

\paragraph{R033 Create Project: Process Methodology}
The process methodology of the Project is selectable 

\paragraph{R034 Create Project: Programming Language}
The programming language of the Project is selectable 

\paragraph{R035 Create Project: Platform}
The platform of the Project is selectable 

\paragraph{R036 Create Project: Industry Sector}
The industry sector of the Project is selectable 

\paragraph{R037 Create Project: Architecture}
The architecture of the Project is selectable 

\paragraph{R038 Create Project: Project Icon}
The project icon of the Project is selectable 

\paragraph{R039 Create Project: Guided Creation Process}
It is possible to start a guided creation for the project which guides the user through each step

\paragraph{R040 Create Project: List Creation}
It is possible to create a new project with a list creation which inherits all properties for the creation

\paragraph{R041 Create Project: Long Project Name}
Project names have to be limited to 40 characters

\paragraph{R042 Create Project: Preselected Properties}
One value must be preselected for all properties.

\paragraph{R043 Create Project: description}
It should be possible to add a project description

\paragraph{R044 Create Project: Property Sorting}
All Properties are sorted alphabetically descending for the selection

\paragraph{R045 Create Project: Suggest Estimation Method}
There should be the possibility to calculate the best fitting estimation method for the project

\paragraph{R046 Create Project: Suggest Estimation Method - Sorting}
The suggested methods are sorted after the best fitting

\subsection{Related Projects}
\paragraph{R009 Find Related Projects}
It must be possible to find related projects.
\paragraph{R010 Load Components From Other Projects}
It is possible to copy Components from other projects into the actual project.



\section{Non-Functional Requirements}
This section describes all non-functional requirements of the application.
\paragraph{R009 Design Guidelines}
The application must fulfills the Design Guidelines from Google - Material Design.
\paragraph{R010 Save Changes Automatically}
All changes in the application need to saved automatically.